\section*{Undergraduate Studies}

I began my undergraduate studies in the computer science specialization program with a math minor.
From the outset, I took honours equivalent of all the math requirements,
where courses are oriented towards proofs and methodology rather than applications.
As a payoff, I applied to and was admitted to the Honours program in my second year,
with math major and computer science minor.

Starting from 2019, while maintaining a full enrolment in my undergraduate courses,
I worked as a research assistant in the linguistic department of the University of Alberta for 1.5 years,
under the supervision of Dr. Antti Arppe, a computational linguist in the University of Alberta.
My responsibility was software development and infrastructure maintenance on indigenous language technologies.
I also helped on the research on finite-state transducers applied to
the generation and parsing of highly inflectional indigenous language local to North America.
From the work experience,
I gained hands-on experience in assorted aspects of software development and valuable social skills with colleagues.

Academically, I had a hiccup in my fourth year,
when I tried to start an online business with applied machine learning.
I developed and operated soundgone.com (now taken down) which was a paid service that isolates and removes instrument/vocal sound
from music sources.
The inspiration for the business was from myself, as I am a drummer by hobby and I believed that
the need for backing tracks was large in demand.
I ended up spreading myself too thin and couldn't maintain good academic standing
while working for my own business and as a research assistant at the same time.
As a consequence, as shown in the transcript,
I failed a lot of courses in the academic year of 2020 and had to drop from the Honours program to a general science program.

I eventually stopped the business too in late 2021, as it wasn't able to provide a net profit.
The experience was personally traumatic to me and brought me immense pressure back then.
Yet I learned valuable lessons in time management and was able to overcome the difficulties.

I eventually fought back on track,
finishing my last undergraduate course in the winter of 2021.
Considering my overall GPA and advanced course selections,
rather than the current program (General Mathematics) listed on the transcript,
the school allows me to graduate with a B.Sc. in Math Specialization,
which has stricter GAP requirements and stricter course requirements consisting of more math courses.
I have requested proof statements from the school of the degree change and completion,
yet the school informs me that this won't show up on the transcript until late May 2022,
when I will receive a certification of my undergraduate degree.
To that end, I have attached my correspondence with the advisor in the Science department of University of Alberta
in the transcript file.
