%! Author = Matt
%! Date = 2022-02-13

% Preamble
\RequirePackage{shellesc}
\documentclass[11pt]{article}

% Packages
\usepackage{csquotes}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=0.9in]{geometry}
% Document
\begin{document}

    Hi, People at the University of Sheffield!

    My name is Siyuan Yan,
    and I preferred the name Matt to avoid unnecessary tongue-twisting.
    I have broad interests in math and computer science.
    I code both as a hobby and in work, and I'm a contributor and creator of numerous projects
    \footnote{My GitHub account: \url{https://github.com/Madoshakalaka}}.

    In the meantime, I'm fascinated by the interaction between computer science and mathematics,
    the major areas being numerical methods, combinatorics, and theorem provers.

    I acknowledge I have a lacking GPA of 2.81/4.0, yet I don't think it's a faithful reflection of my ability,
    as it's due to extraneous personal conditions in the year 2020.
    It's my sincere wish that my all around skills and strong research interest be considered.

    \input{../../fragments/short-undergrad}

    \input{../../fragments/language-skills}

    \input{../../fragments/research-interest-hott-and-proof-assist}


    Despite my research interests, I'm not best-prepared, and I'd love to learn more about various aspects of the field
    before pursuing a more focused career of research in the future.
    Algebra, in particular, is of much interest to me and is what I want to learn more about in the University of Sheffield.

    \input{../../fragments/math-courses}

    With all the excitement I have,
    I crave an opportunity to study more at Sheffield University before I can contribute to academia
    , and I look forward to a new chapter of my life in Cardiff in the upcoming fall term.

\end{document}
