%! Author = Matt
%! Date = 2022-02-13

% Preamble
\RequirePackage{shellesc}
\documentclass[11pt]{article}

% Packages
\usepackage{csquotes}
\usepackage{hyperref}
% Document
\begin{document}

    Hi, People at Wesleyan University!

    My name is Siyuan Yan,
    and I preferred the name Matt to avoid unnecessary tongue-twisting.
    I have broad interests in math and computer science.
    Coding and open-source has been my hobby since high school,
    in the meantime, doing academic research has always been my life goal.

    I must apologize to have applied in this late time.
    Actually Wesleyan University is the first graduate school I am applying to.
    And I promise this is an honest and sincere letter of mine.

    \input{../../fragments/undergrad}

    \input{../../fragments/research-interest-hott-and-proof-assist}

    With all the excitements I have,
    I crave an opportunity to study more about the relavant fields
    in Wesleyan University before I can contribute to the research.
    During my search for ideal supervisors,
    I found Dr. Daniel R. Licata \footnote{\url{https://dlicata.wescreates.wesleyan.edu/}} in the
    authors of the HoTT book\footnote{\url{https://homotopytypetheory.org/book/}},
    I believe he can be an ideal mentor for my further studies,
    or at least, a person I can turn to in my path of graduate studies.


    I sincerely hope my application be thoroughly considered.
    Please feel free to ask any further questions via my email \href{mailto:syan4@ualberta.ca}{syan4@ualberta.ca}.

\end{document}
