\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Siyuan Yan ( Matt Yan )}}\\
	syan4@ualberta.ca $\cdot$ https://madoshakalaka.github.io/\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{University of Alberta}\hfill Edmonton, Alberta\\
BSc with Specialization in Mathematics \hfill Sep 2016 - Dec 2021\\
\vspace{2mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Neptish Inside} \hfill https://neptishinside.com/\\
\textit{Fullstack Web Developer} \hfill Sep 2021 - Oct 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
\item Commissioned work, website for J-Star Motion Corporation, featuring a fully Rusty stack (Axum backend and Yew frontend).
\end{itemize}

\textbf{Soundgone}\\
\textit{Founder} \hfill Sep 2019 - June 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
\item Website and related paid services that generate tracks for practice or performance from audio files by isolating or removing selected elements from a song.
\end{itemize}
\textbf{University of Alberta, Linguistic Department, ALTLAB} \hfill Edmonton, Alberta\\
\textit{Research Assistant} \hfill May 2019 - December 2020\\
\hfill https://itwewina.altlab.app/\\
\hfill https://altlab.ualberta.ca/\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Web-oriented software development and infrastructure maintenance on indigenous language technologies.
	Research on finite-state transducers applied to the generation and parsing of highly inflectional indigenous languages local to North America.
\end{itemize}


\header{Skills}
\begin{tabular}{ l l }
	Communication:               & Very Good written English, Native level spoken English \\
	Programming Languages:       & Python, Rust, Typescript/Javascript, Java              \\
	Daily Linux User:            & Good Scripting Skills                                  \\
	Multimedia:                  & proficient with Photoshop/Premiere/Gimp etc.           \\
	I write everything in latex: & including this resume :)                               \\
\end{tabular}
\vspace{2mm}

\header{Projects}
{\textbf{Blackjack Card Counter}} {\sl Embeded Micro-controller, Combinatorics, Probability, Java} \\
Independent project that helps to play casino game blackjack. The phone app receives information from two Bluetooth sensors installed in shoes and communicates with a server to indicate the user the best play strategy using phone vibration. Simulation results showed the app gives a significant edge towards the player.\\
\vspace*{2mm}
{\textbf{Web Forum}} {\sl AWS ( Amazon Web Services ), Python} \\
Independent project. A craigslist-like advertisement website oriented to the Chinese community which offers anonymous posting and communication.\\
\vspace*{2mm}
{\textbf{Cloud Based Machine Learning Inference}} {\sl Tensorflow} \\
Collaborated academic project. Provides online virtual glass fitting with user submitted face photos. Implemented the file download/upload handling and browser-end 3D rendering. Bridged the model inference with the web server.\\
\vspace*{2mm}
{\textbf{Cloud Based Machine Learning Inference on Video Streaming}} {\sl Tensorflow, YOLO, Microsoft Azure} \\
Collaborated academic project. Provides real time traffic sign detection where the client streams traffic video to the server and receives detection results. Implemented the the server and client side back-end. Implemented performance measurement and analysis tools with the client and the server.\\
\vspace*{2mm}
{\textbf{League of Legneds Assistance}} {\sl Python, OpenCV} \\
Independent project. A program that processes video stream from the online game League of Legends and responds in realtime. Achieved a win rate of \textasciitilde{}70\% in lower competitive elo.\\
\vspace*{2mm}
{\textbf{Open-Source Projects}}\hfill https://github.com/Madoshakalaka\\
I contribute to a variety of open-source projects. Notably I\textquotesingle{}m the creator of pipenv-setup, a utility that helps manage dependency and the packaging process of pipenv projects, and the creator of yew-interop, a library that helps asyncrously loading resources in the Yew frontend framework written in Rust.\\
\vspace*{2mm}

\header{Awards}
\textbf{International Student Scholarship} \hfill The University of Alberta\\
An scholarship awarded to outstanding international applicants \hfill Sep 2016\\
\vspace*{2mm}

\ 
\end{document}