\section*{Undergraduate Studies}

I began my undergraduate studies in the computer science specialization program with a math minor.
From the outset, I took honours equivalent of all the math requirements,
As a payoff, I applied to and was admitted to the Honours program in my second year,
with math major and computer science minor.

Starting from 2019, while maintaining a full enrolment in my undergraduate courses,
I worked as a research assistant in the linguistic department of the University of Alberta
under the supervision of Dr. Antti Arppe, a computational linguist in the University of Alberta.
The work experience added a lot to my hands-on experience in software development and valuable social skills.

Academically, I had a hiccup in my fourth year,
when I tried to start an online business with applied machine learning.
I founded and operated soundgone.com (now taken down) which was a paid service that isolates and removes instrument/vocal sound
from music sources.
The inspiration for the business was from me, as I am a drummer by hobby and I believed that
the need for backing tracks was large in demand.
However, I ended up spreading myself too thin and couldn't maintain good academic standing
while working for my own business and as a research assistant at the same time.
As a consequence, as shown in the transcript,
I failed several courses in the academic year of 2020 and had to drop from the Honours program to a general science program.

The experience was personally traumatic to me and brought me immense pressure back then.
Yet I learned valuable lessons in time management and was able to overcome the difficulties eventually,
finishing my last undergraduate course in the winter of 2021.
Considering my overall GPA,
rather than the current program (General Mathematics) listed on the transcript,
the school allows me to graduate with a B.Sc. in Math Specialization,
which has stricter GAP requirements and stricter course requirements consisting of a curriculum of more math courses.
