%! Author = Matt
%! Date = 2022-02-13

% Preamble
\RequirePackage{shellesc}
\documentclass[11pt]{article}

% Packages
\usepackage{csquotes}
\usepackage[hidelinks]{hyperref}
% Document
\begin{document}

    Hi, People at Imperial College London!

    My name is Siyuan Yan,
    and I preferred the name Matt to avoid unnecessary tongue-twisting.
    I have broad interests in math and computer science.
    I code both as a hobby and in work, and I'm a contributor and creator of numerous projects
    \footnote{My GitHub account: \url{https://github.com/Madoshakalaka}}.

    In the meantime, I'm fascinated by the interaction between computer science and mathematics,
    the major areas being numerical methods, combinatorics, and theorem provers.

    I acknowledge I have a lacking GPA of 2.81/4.0, yet I don't think it's a faithful reflection of my ability.
    I'll explain the extraneous situation I went through below,
    and It's my sincere wish that my all around skills and strong research interest be considered.


    \input{../../fragments/undergrad}

    \input{../../fragments/language-skills}

    \input{../../fragments/research-interest-hott-and-proof-assist}

    With all the excitements I have,
    I crave an opportunity to study more about the relevant fields
    at Imperial College London before I can contribute to the research.

    I sincerely hope my application be thoroughly considered.
    Please feel free to ask any further questions via my email \href{mailto:syan4@ualberta.ca}{syan4@ualberta.ca} or
    Skype.

\end{document}
